Cross-Validation Default

### 2025-03-10 minos/validation/cross_validation_default.Rmd

# cv simulation batches
cv.simul.files1 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch1'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw1 <- do.call(rbind, lapply(cv.simul.files1, read.csv))
cv.simul.files2 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch2'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw2 <- do.call(rbind, lapply(cv.simul.files2, read.csv))
cv.simul.files3 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch3'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw3 <- do.call(rbind, lapply(cv.simul.files3, read.csv))
cv.simul.files4 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch4'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw4 <- do.call(rbind, lapply(cv.simul.files4, read.csv))
cv.simul.files5 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch5'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw5 <- do.call(rbind, lapply(cv.simul.files5, read.csv))

@@

# SF_12_MCS

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12_MCS')
multi_year_boxplots(raw, cv, 'SF_12_MCS')
snapshot_OP_plots(raw, cv, 'SF_12_MCS', target.years = c(2015, 2017, 2019, 2021))
q_q_comparison(raw, cv, 'SF_12_MCS')
```
```{r}
sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2015)
print(sf12.14)
```
```{r}
sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2017)
print(sf12.16)
```
```{r}
sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2019)
print(sf12.18)
```
```{r}
sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2021)
print(sf12.20)
rm(sf12.14, sf12.16, sf12.18, sf12.20)
```

>>>>

# cv simulation batches
cv.simul.files1 <- list.files(here::here('data', 'imputed_final_US', 'cross_validation', 'batch1'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw1 <- do.call(rbind, lapply(cv.simul.files1, read.csv))
cv.simul.files2 <- list.files(here::here('data', 'imputed_final_US', 'cross_validation', 'batch2'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw2 <- do.call(rbind, lapply(cv.simul.files2, read.csv))
cv.simul.files3 <- list.files(here::here('data', 'imputed_final_US', 'cross_validation', 'batch3'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw3 <- do.call(rbind, lapply(cv.simul.files3, read.csv))
cv.simul.files4 <- list.files(here::here('data', 'imputed_final_US', 'cross_validation', 'batch4'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw4 <- do.call(rbind, lapply(cv.simul.files4, read.csv))
cv.simul.files5 <- list.files(here::here('data', 'imputed_final_US', 'cross_validation', 'batch5'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw5 <- do.call(rbind, lapply(cv.simul.files5, read.csv))

@@

# SF_12

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12')
multi_year_boxplots(raw, cv, 'SF_12')
snapshot_OP_plots(raw, cv, 'SF_12', target.years = c(2015, 2017, 2019, 2021))
q_q_comparison(raw, cv, 'SF_12')
```
```{r}
sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2015)
print(sf12.14)
```
```{r}
sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2017)
print(sf12.16)
```
```{r}
sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2019)
print(sf12.18)
```
```{r}
sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2021)
print(sf12.20)
rm(sf12.14, sf12.16, sf12.18, sf12.20)
```
